Computational musicology, ????, Profit

### 2016-07-31 paper.tex
Strange Loop has a space.
Cite Algorave.

Coutinho et al. resolve this ``puzzling old problem" a different way. They observe that while in biology ``fossils can be studied
to understand the
past and evolution of species", music lacks a corresponding natural object for them to base their research
upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
to make their work ``scientifically sound".

This paper/essay however, attempts to resolve the tension that Minsky observed between a scientific and cultural approach to
musical study by beginning with complexity theory and then building upon that to consider literary and musical works. The
informal and literary style is not just for fun (though I hope that it is that), but is also attempt to show how computational
musicology might function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.

@@

Thank you to the StrangeLoop conference of 2015, which accepted the talk `Kolmogorov Music' from which this paper derives.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Online Library of Babel} Basile, Jonathan: \verb|libraryofbabel.info|, \url{https://libraryofbabel.info}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: Computational	Musicology:	An Artificial Life Approach \textit{Proceedings of the 2nd Portuguese Workshop on Artiﬁcial Life and Evolutionary Algorithms Workshop}, 2005.
\bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{The Digital Computer as a Musical Instrument} Mathews, Max Vernon, \textit{Science}, volume 142, number 11, 1963.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{Music Mind and Meaning} Minsky, Marvin: Music, Mind, and Meaning, \textit{Computer Music Journal}, volume 5, number 3, Fall 1981.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Intrinsic Plaguerism Detection} Seaward, Leanne and Matwin, Stan: Intrinsic Plagiarism Detection using Complexity Analysis, \textit{PAN'09}, 2009.
\bibitem{Two Cultures} Snow, Charles Percy: The Two Cultures and the Scientific Revolution, \textit{Cambridge University Press}, 1959.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

>>>>

Coutinho et al. resolve what they refer to as the ``puzzling old problem" a different way. They observe that while in biology
``fossils can be studied to understand the
past and evolution of species", music lacks a corresponding natural object for them to base their research
upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
to make their work ``scientifically sound" (their words).

On a practical level, algorave musicians are already well advanced in finding a solution to the ``problem" of reconciling
computation with creative practice\cite{Algorave}. These performers generate music by writing code in front of a live audience.
They explore the
potential and the limits of programming as a musical instrument. For them, live coding is a challenge of language and expression.
If the praxis of programming and musical performance can be fruitfully combined, then surely literary and scientific theory
might also be brought together.

This paper/essay attempts to resolve the tension that Minsky observed between the scientific and the cultural approach to
studying music by taking complexity theory and then building upon it to consider literary and musical works. The
informal and literary style is not just for fun (though I hope that it is that), but is also attempt to show how computational
musicology might function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.

@@

Thank you to the Strange Loop conference of 2015, which accepted the talk `Kolmogorov Music' from which this paper derives.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Online Library of Babel} Basile, Jonathan: \verb|libraryofbabel.info|, \url{https://libraryofbabel.info}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Algorave} Cheshire, Tom: Hacking meets clubbing with the `algorave', \textit{Wired}, August 29, 2013.
\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: Computational	Musicology:	An Artificial Life Approach, \textit{Proceedings of the 2nd Portuguese Workshop on Artiﬁcial Life and Evolutionary Algorithms Workshop}, 2005.
\bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{The Digital Computer as a Musical Instrument} Mathews, Max Vernon, \textit{Science}, volume 142, number 11, 1963.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{Music Mind and Meaning} Minsky, Marvin: Music, Mind, and Meaning, \textit{Computer Music Journal}, volume 5, number 3, Fall 1981.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Intrinsic Plaguerism Detection} Seaward, Leanne and Matwin, Stan: Intrinsic Plagiarism Detection using Complexity Analysis, \textit{PAN'09}, 2009.
\bibitem{Two Cultures} Snow, Charles Percy: The Two Cultures and the Scientific Revolution, \textit{Cambridge University Press}, 1959.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
